RUPEE: A fast and accurate purely geometric protein structure search

### 2019-01-06 docs/rupee_2.tex
region plots

The polar plot described above is used to define torsion angle regions for each secondary structure assignment. 
The eight DSSP secondary structure assignment codes defined in \cite{Kabsch1983} divide into three groups in which torsion angle regions are roughly the same: `G',`H',`I', and `T' corresponding to $3_{10}$-helix, $\alpha$-helix, $\pi$-helix, and turn, respectively; `E' and `B' corresponding to $\beta$-strand and $\beta$-bridge, respectively; and `S' and `C' corresponding to bend and coil, respectively.

Polar plots for each group of DSSP assignment codes along with defined region and descriptor designations are shown in \figurename~\ref{fig:regions}, with the exception of turns and bridges, which receive descriptors 11 and 12, respectively. 
For each polar plot, there are well-defined continuous regions of torsion angles that remain continuous in the plots. 
The only exception is found in the bends and coil plot at $\psi = 60\degree$ between $\phi = -180\degree$ and $\phi = 0\degree$.

>>>>

The polar plot described above is used to define torsion angle regions for DSSP secondary structure assignments.
We divide six of the eight DSSP secondary structure assignment codes defined in \cite{Kabsch1983} into three groups: helices (`G',`H',`I'), strands (`E'), and bends and coils (`S',`C').
For each of the three groups, we plotted the torsion angles and identified regions into which they clustered as shown in \figurename~\ref{fig:regions}.
The regions for helices are assigned descriptors 1 to 4, for strands 5 to 7, and for bends and coils 8 to 10. 
The other two DSSP secondary structure assignments codes for turns (`T') and bridges~(`B'), are assigned descriptors 11 and 12, respectively.
For each polar plot, there are well-defined continuous regions of torsion angles that remain continuous in the plots. 
The only exception is found in the bends and coils plot at $\psi = 60\degree$ between $\phi = -180\degree$ and $\phi = 0\degree$.
